Digital History in Finland, 1488-1828

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=5}
top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")
```

>>>>

```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=4}
top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")
```
